Trends of SDR in Thessaloniki

### 2023-10-08 Article.Rmd
Commit 2023-10-08 21:09

```{r cusumnotrend, echo = FALSE, fig.cap='Running cumulative sum plots of the daily SDR after removing the long term trend from the daily values, for the three different sky conditions.', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeDailyCuSumNOtrend-1.png",    # ALL sky
    "./images/CumulativeDailyCuSumNOtrend-5.png",    # CLEAR sky
    "./images/CumulativeDailyCuSumNOtrend-9.png"))   # Cloud sky
```

<!-- ```{r cusumnotrendmonthly, echo = FALSE, fig.cap='Running cumulative sum plots of the monthly SDR after removing the long term trend from the monthly values, for the three different sky conditions.', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3} -->
<!-- knitr::include_graphics(c( -->
<!--     "./images/CumulativeMonthlyCuSum",    # ALL sky -->
<!--     "./images/CumulativeMonthlyCuSumNOtrend-5.png",    # CLEAR sky -->
<!--     "./images/CumulativeMonthlyCuSumNOtrend-9.png"))   # Cloud sky -->
<!-- ``` -->

>>>>

```{r cusumnotrend, echo = FALSE, fig.cap='Running cumulative sum plots of the daily SDR after removing the long term trend from the daily values.', fig.subcap=c('All-skies.', 'Clear-skies.', 'Cloud-skies.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeDailyCuSumNOtrend-1.png",    # ALL sky
    "./images/CumulativeDailyCuSumNOtrend-5.png",    # CLEAR sky
    "./images/CumulativeDailyCuSumNOtrend-9.png"))   # Cloud sky
```

```{r cusumnotrendmonthly, echo = FALSE, fig.cap='Running cumulative sum plots of the monthly SDR after removing the long term trend from the monthly values.', fig.subcap=c('All-skies.', 'Clear-skies.', 'Cloud-skies.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeMonthlyCuSumNOtrend-1.png",    # ALL sky
    "./images/CumulativeMonthlyCuSumNOtrend-5.png",    # CLEAR sky
    "./images/CumulativeMonthlyCuSumNOtrend-9.png"))   # Cloud sky
```
